The problem and promise of scale in animal social multilayer networks

### 2020-02-10 paper/manuscript.Rmd
fig captions

We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals, importance of individual layers and the similarity of
different layers. To measure the role of individuals, we calculated degree
centrality and graph strength. Degree centrality is the number of direct
connections an individual has to other individuals in a network layer. Graph
strength is the degree weighted by the strength of association, in this case
SRI, in each layer-specific season and landcover context <!-- TODO: citation for
graph strength?-->. Extending degree centrality, we calculated multidegree, the
sum of degree centrality across layers, and neighbourhood, the sum of unique
neighbours to each individual [@Berlingerio_2012; @Kivela_2014]. We evaluated
the relevance and redundancy of layers by combining the multidegree and
neighbourhood to calculate connective redundancy and layer relevance. Connective
redundancy is the proportion of neighbours repeated in multiple layers, and
layer relevance is the proportion of neighbours present in each layer compared
to the neighbourhood for each individual [@Berlingerio_2012]. Finally, we
calculated the similarity of layers between seasons, across landcover classes
(e.g.: winter open compared to summer open) using the Pearson correlation
coefficient [@Br_dka_2018].

@@

(ref:socres) Varying scale in social threshold. For each social threshold, multilayer
networks were constructed for each landcover class (forest, lichen and open)
across two seasons (summer and winter) and four network metrics calculated.  A)
Mean graph strength across individuals showed an increase for winter network
layers at 50 m through 500 m while summer network layers had consistently weak
connections. B) Mean layer relevance was relatively stable across social
thresholds for each season and landcover layer. C) Similarity of landcover
network layers between seasons (e.g.: open summer compared to open winter)
showed different responses to changing landcover scale with an overall increase
in similarity for open layers and decrease in similarity for lichen layers.
<!--TODO: what about forest.--> D) Mean connective redundancy across individuals
increased rapidly between 5 m and 50 m reaching a plateau  of about 0.65 at
approximately a 50 m <!--TODO:**??**--> social threshold before decreasing
between 400 m and 500 m.

@@

(ref:lcres) Variation in multilayer network metrics as a function of changes in
landcover resolution, a metric which we interpret as spatial scale. For each
landcover resolution, multilayer networks
were constructed for each landcover class (forest, lichen and open) across two
seasons (summer and winter), and four network metrics were calculated and we
examined how network metrics changed as a function of changes in spatial scale.
A) Mean graph strength of individuals was weaker during the summer compared to
the winter months. B) Mean layer relevance showed sparse connectivity in summer
compared to winter networks and a decrease in winter lichen layer relevance at
higher landcover resolutions. C) Similarity of landcover network layers between
seasons (e.g.: open summer compared to open winter) showed different responses
to changing landcover scale with an increase in similarity for forest layers at
250 m and decrease in similarity for open layers at 250 m. Note that lichen
layer similarity is not shown because individuals did not interact in lichen
habitats greater greater than 10 m landcover resolution. D) Mean connective
redundancy across individuals showed a decreasing trend with increasing
landcover resolution.

@@

<!-- TODO: RO first sentence... -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number
of observations (10-485 observations in steps of 25) were selected from the
complete data set to construct multilayer networks with layers defined by each
landcover class (forest, lichen and open) across two seasons (summer and winter)
and four network metrics calculated. A) Mean graph strength across individuals
varied for winter layers becoming relatively stable at 200 observations and
remained weak throughout for summer layers. B) Mean layer relevance across
individuals increased for winter layers and slightly increased for summer
layers. C) Similarity of landcover network layers between seasons (e.g.: open
summer compared to open winter) showed a stabilizing layer similarity at 200
observations for forest and 300 observations for lichen and open.
<!--TODO:*There were observations of individuals in lichen and open areas at
lower numbers of observations during the winter, so layer similarity could not
be calculated at these values.* **Brief explanation of why two landcover don't
have values at lower nobs??**.--> D) Mean connective redundancy across
individuals increased with increasing number of observations, which begins to
plateau around 100 observations.

@@

(ref:winlen) Varying scale in time window length. For each time window length
(40 to 100 days in length increasing by 5 days in sequence), multilayer networks
were constructed for each landcover class (forest, lichen and open) across two
seasons (summer and winter) and four network metrics calculated. A) Mean graph
strength across individuals was relatively stable over increasing time window
lengths, though there was more variation in strength between landcover types as
window length increased. <!--TODO:**[see if you agree with my changes. B-D were
based off fig. 3 and not relevant to this figure]**-->  B) Mean layer relevance
generally increased during the summer months but was relatively stable across
time window lengths for each landcover layer. C) Similarity of landcover network
layers between seasons (e.g.: open summer compared to open winter) showed
increasing similarity consistent across landcover layers with increasing window
length. D) Mean connective redundancy across individuals varied dramatically
depending on the length of the time window <!--TODO:**[JWT: previously this was
describing fig. 3. I don't know if what I wrote best encapsulates what
connnective redundancy does here. Length of time window seems to make connective
redundancy highly variable as it changes.]**.-->

@@

(ref:winpos) Varying scale in time window position. For each time window
position (shifting the start date of the time window used to define seasons 1 to
48 days from the original), multilayer networks were constructed for each
landcover class (forest, lichen and ope) across two seasons (summer and winter)
and four network metrics calculated. A) Mean graph strength across individuals
increased in summer network layers at window position 25 and increased between
window position 20 and 40 for winter network layers. B) Mean layer relevance
slightly decreased for winter layers and increased for summer layers, showing
decreasing connectivity in shifted winter time windows and greater connectivity
in summer layers at later window positions. C) Similarity of landcover network
layers between seasons (e.g.: open summer compared to open winter) showed
fluctuations in layer similarity across landcover types with shifted time
windows. <!--TODO:**[JWT: previously describing window length, not position.
Check that you're ok with my changes]**--> D) Mean connective redundancy across
individuals increased between window position 12 through 48 due to increased
connectivity in the summer network layers.

>>>>

We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals, importance of individual layers and the similarity of
different layers. To measure the role of individuals, we calculated degree
centrality and graph strength. Degree centrality is the number of direct
connections an individual has to other individuals in a network layer. Graph
strength is the degree weighted by the strength of association, in this case
SRI, in each layer-specific season and landcover context <!-- TODO: citation for
graph strength?-->. Extending degree centrality, we calculated multidegree, the
sum of degree centrality across layers, and neighbourhood, the sum of unique
neighbours to each individual [@Berlingerio_2012; @Kivela_2014]. We evaluated
the relevance and redundancy of layers by combining the multidegree and
neighbourhood to calculate connective redundancy and layer relevance. Connective
redundancy is the proportion of neighbours repeated in multiple layers, and
layer relevance is the proportion of neighbours present in each layer compared
to the neighbourhood for each individual [@Berlingerio_2012]. Finally, we
calculated the similarity of layers between seasons, across landcover classes
(e.g. winter open compared to summer open) using the Pearson correlation
coefficient [@Br_dka_2018].

@@

<!-- Figure 3: metrics by social scale -->
(ref:socres) Varying scale in social threshold. For each social threshold, multilayer
networks were constructed for each landcover class (forest, lichen and open)
across two seasons (summer and winter) and four network metrics calculated.  A)
Mean graph strength across individuals showed an increase for winter network
layers at 50 m through 500 m while summer network layers had consistently weak
connections. B) Mean layer relevance was relatively stable across social
thresholds for each season and landcover layer. C) Similarity of landcover
network layers between seasons (e.g. open summer compared to open winter)
showed different responses to changing landcover scale with an overall increase
in similarity for open layers and decrease in similarity for lichen layers.
<!--TODO: what about forest.--> D) Mean connective redundancy across individuals
increased rapidly between 5 m and 50 m reaching a plateau  of about 0.65 at
approximately a 50 m <!--TODO:**??**--> social threshold before decreasing
between 400 m and 500 m.

@@

<!-- Figure 4: metrics by landcover resolution -->
(ref:lcres) Variation in multilayer network metrics as a function of changes in
landcover resolution, a metric which we interpret as spatial scale. For each
landcover resolution, multilayer networks were constructed for each landcover
class (forest, lichen and open) across two seasons (summer and winter), and four
network metrics were calculated and we examined how network metrics changed as a
function of changes in spatial scale. A) Mean graph strength of individuals was
weaker during the summer compared to the winter months. B) Mean layer relevance
showed sparse connectivity in summer compared to winter networks and a decrease
in winter lichen layer relevance at higher landcover resolutions. C) Similarity
of landcover network layers between seasons (e.g. open summer compared to open
winter) showed different responses to changing landcover scale with an increase
in similarity for forest layers at 250 m and decrease in similarity for open
layers at 250 m. Note that lichen layer similarity is not shown because
individuals did not interact in lichen habitats greater greater than 10 m
landcover resolution. D) Mean connective redundancy across individuals showed a
decreasing trend with increasing landcover resolution.

@@

<!-- Figure 5: metrics by number of observations -->
<!-- TODO: RO first sentence... -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number
of observations (10-485 observations in steps of 25) were selected from the
complete data set to construct multilayer networks with layers defined by each
landcover class (forest, lichen and open) across two seasons (summer and winter)
and four network metrics calculated. A) Mean graph strength across individuals
varied for winter layers becoming relatively stable at 200 observations and
remained weak throughout for summer layers. B) Mean layer relevance across
individuals increased for winter layers and slightly increased for summer
layers. C) Similarity of landcover network layers between seasons (e.g. open
summer compared to open winter) showed a stabilizing layer similarity at 200
observations for forest and 300 observations for lichen and open.
<!--TODO:*There were observations of individuals in lichen and open areas at
lower numbers of observations during the winter, so layer similarity could not
be calculated at these values.* **Brief explanation of why two landcover don't
have values at lower nobs??**.--> D) Mean connective redundancy across
individuals increased with increasing number of observations, which begins to
plateau around 100 observations.

@@

(ref:winlen) Varying scale in time window length. For each time window length
(40 to 100 days in length increasing by 5 days in sequence), multilayer networks
were constructed for each landcover class (forest, lichen and open) across two
seasons (summer and winter) and four network metrics calculated. A) Mean graph
strength across individuals was relatively stable over increasing time window
lengths, though there was more variation in strength between landcover types as
window length increased. <!--TODO:**[see if you agree with my changes. B-D were
based off fig. 3 and not relevant to this figure]**-->  B) Mean layer relevance
generally increased during the summer months but was relatively stable across
time window lengths for each landcover layer. C) Similarity of landcover network
layers between seasons (e.g. open summer compared to open winter) showed
increasing similarity consistent across landcover layers with increasing window
length. D) Mean connective redundancy across individuals varied dramatically
depending on the length of the time window <!--TODO:**[JWT: previously this was
describing fig. 3. I don't know if what I wrote best encapsulates what
connnective redundancy does here. Length of time window seems to make connective
redundancy highly variable as it changes.]**.-->

@@

(ref:winpos) Varying scale in time window position. For each time window
position (shifting the start date of the time window used to define seasons 1 to
48 days from the original), multilayer networks were constructed for each
landcover class (forest, lichen and ope) across two seasons (summer and winter)
and four network metrics calculated. A) Mean graph strength across individuals
increased in summer network layers at window position 25 and increased between
window position 20 and 40 for winter network layers. B) Mean layer relevance
slightly decreased for winter layers and increased for summer layers, showing
decreasing connectivity in shifted winter time windows and greater connectivity
in summer layers at later window positions. C) Similarity of landcover network
layers between seasons (e.g. open summer compared to open winter) showed
fluctuations in layer similarity across landcover types with shifted time
windows. <!--TODO:**[JWT: previously describing window length, not position.
Check that you're ok with my changes]**--> D) Mean connective redundancy across
individuals increased between window position 12 through 48 due to increased
connectivity in the summer network layers.
